Concurrent Programming with Harmony

### 2020-08-21 book/paper.tex
Latest

\section*{Exercises}
\begin{problems}
\item Draw additional states and steps in \autoref{fig:rdwr}
for three processes.
\item Optimize your solutions to \autoref{ex:qcontains} to use reader/writer locks.
\item \label{ex:boundlock} Using busy waiting, implement a ``bound lock'' that allows
up to \texttt{M} processes to acquire it at the same time.  A bound lock
with \texttt{M == 1} is an ordinary lock.
You should define a constant \texttt{M} and two methods:
\texttt{acquire\_bound\_lock()}
and \texttt{release\_bound\_lock()}.
\item Write a test program for your bound lock
that checks that no more than \texttt{M} processes can acquire the
bound lock.
\end{problems}

@@

\section*{Exercises}
\begin{problems}
\item \label{ex:nbproduce} Change the code in \autoref{fig:boundedbuffer} so that
\texttt{produce()} fails if the buffer is full rather than block.
\texttt{produce()} should return \texttt{False} if it fails
and return \texttt{True} if it succeeds.
\item Implement a \emph{bounded stack}.  Method \texttt{push}(\textit{item})
should block if the stack is full.  Method \texttt{pop()} should block
until the stack is non-empty and then return an item.
Also implement test programs for your solution.
\item \label{ex:gpu} Implement a thread-safe \emph{GPU allocator} by modifying
\autoref{fig:gpu}.
There are \texttt{N} GPUs identified by the numbers
1 through \texttt{N}.  Method \texttt{gpuAlloc()} returns the identifier
of an available GPU, blocking if there is currently no available GPU.
Method \texttt{gpuRelease}(\textit{gpu}) releases the given GPU.  It never needs
to block.
\end{problems}

@@

@@

So far we have concentrated on critical sections to synchronize multiple
processes.  Certainly, preventing multiple processes from accessing
certain code at the same time simplifies how to think about synchronization.
However, it can lead to starvation.  Even in the absence of starvation,
if some process is slow for some reason while being in the critical section,
the other processes have to wait for it to finish executing the critical section.
In this chapter, we will have a look at how one can develop concurrent
code in which processes do not have to wait for other processes to complete their
ongoing operations.

>>>>

\section*{Exercises}
\begin{problems}
\item Draw additional states and steps in \autoref{fig:rdwr}
for three processes.
\item Optimize your solutions to \autoref{ex:qcontains} to use reader/writer locks.
\item \label{ex:boundlock} Using busy waiting, implement a ``bound lock'' that allows
up to \texttt{M} processes to acquire it at the same time.  A bound lock
with \texttt{M == 1} is an ordinary lock.
You should define a constant \texttt{M} and two methods:
\texttt{acquire\_bound\_lock()}
and \texttt{release\_bound\_lock()}.
(Bound locks are useful for situations where too many processes working
at the same time might exhaust some resource such as a cache.)
\item Write a test program for your bound lock
that checks that no more than \texttt{M} processes can acquire the
bound lock.
\end{problems}

@@

\section*{Exercises}
\begin{problems}
\item \label{ex:nbproduce} Change the code in \autoref{fig:boundedbuffer} so that
\texttt{produce()} fails if the buffer is full rather than block.
\texttt{produce()} should return \texttt{False} if it fails
and return \texttt{True} if it succeeds.
\item Optimize the code in \autoref{fig:boundedbuffer} for the case
where there is only one consumer and one producer.
\item Implement a \emph{bounded stack}.  Method \texttt{push}(\textit{item})
should block if the stack is full.  Method \texttt{pop()} should block
until the stack is non-empty and then return an item.
Also implement test programs for your solution.
\item \label{ex:gpu} Implement a thread-safe \emph{GPU allocator} by modifying
\autoref{fig:gpu}.
There are \texttt{N} GPUs identified by the numbers
1 through \texttt{N}.  Method \texttt{gpuAlloc()} returns the identifier
of an available GPU, blocking if there is currently no available GPU.
Method \texttt{gpuRelease}(\textit{gpu}) releases the given GPU.  It never needs
to block.
\end{problems}

@@

(Another option is to use synchronization techniques that do not use locks.
See \autoref{ch:nonblocking} for more information.)

@@

So far we have concentrated on critical sections to synchronize multiple
processes.  Certainly, preventing multiple processes from accessing
certain code at the same time simplifies how to think about synchronization.
However, it can lead to starvation.  Even in the absence of starvation,
if some process is slow for some reason while being in the critical section,
the other processes have to wait for it to finish executing the critical section.
Also, using synchronization primitives in interrupt handlers is tricky
to get right (\autoref{ch:interrupts}) and might run too long.
In this chapter, we will have a look at how one can develop concurrent
code in which processes do not have to wait for other processes to complete their
ongoing operations.
